A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-01-25 rebuttal_responses_revision1.tex

\documentclass[preprint,12pt]{elsarticle}
% major revision and answer question (3 reviewers)
%Sunday, January 24⋅22:30 – 22:55
%Daily, until Jan 29, 2021

% mark in blue or red
\usepackage{xcolor}

\newenvironment{MyColorPar}[1]{%
    \leavevmode\color{#1}\ignorespaces%
}{%
}%

\begin{document}

@@

\section{Revision cover letter (cancers-1082127)} % 2021/01/25
%其實直接 online 填寫即可
%Please provide a cover letter to explain point-by-point the details of the revisions [changes 摘要即可 from the rebuttal]  in the manuscript

%Assistant Editor
%E-Mail: aubree.zhu@mdpi.com
%MDPI Branch Office, Tianjin
Assistant Editor of Cancers%\newline

Jan 29, 2021

Dear Dr. Aubree Zhu:

Enclosed, please find our revised manuscript (cancers-1082127) entitled "A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma" by Chi et al., which we wish to be considered for publishing as a research article in Cancers. We greatly appreciate your time in serving as the editor handling this manuscript and also thank the reviewers for their critical comments and suggestions on our manuscript.

We have since performed additional analysis, experiment and revised the manuscript accordingly to address their critical comments and suggestions in a point-by-point manner, 
%{%
1) the description of the rationale that how to pick up the Thymosin Beta-4 X-Linked (TMSB4X) in details, 2) the statistical analysis of MALDI imaging mass spectrometry and 3) the IHC staining with positive and negative control images and further analysis of nuclear TMSB4X staining. 
We re-wrote the introduction in detail and re-examined the tissue microarray slides according to the suggestion by reviewer \#1.
%}

According to the editor's comments, we have the manuscript checked for English grammar and reformat Table 1 by rotating 90 degrees to portrait mode. %（Table 1 轉正)

%{%
According to the reviewers' comments, we added new Figure 1C, 2, S2, S3, and Table S2. We also replaced Figure 3D and 4A with high magnitude images from the same slides. We transferred the original Figure 2 into supplementary Figure S1 to enhance the rationale and removed the old supplementary Table S1.
%}

@@

We wish our revised manuscript could be satisfied and accepted for publication in Cancers. Thanks very much for the kind helps and the reviewers' critical comments.

Kind regards,

Yu-Chuan (Jack) Li, M.D., Ph.D.

Graduate Institute of Biomedical Informatics,

College of Medical Science and Technology,

Taipei Medical University,

Taipei, Taiwan

@@

%2) [cancers-1082127_main_redMarked] 自動化 by latex:
%"Track Changes" function in latex => by latexdiff
%Some options, taken from the documentation, include:
%UNDERLINE—added text is wavy-underlined and blue, discarded text is struck out and red;
%CTRADITIONAL—added text is blue and set in sans-serif, and a red footnote is created for each discarded piece of text;
%TRADITIONAL—like CTRADITIONAL but without the use of colour;
%CFONT—added text is blue and set in sans-serif, and discarded text is red and very small size;
%FONTSTRIKE—added text is set in sans-serif, discarded text small and struck out;
%CHANGEBAR—added text is blue, and discarded text is red. Additionally, the changed text is marked with a bar in the margin.
%https://www.overleaf.com/learn/latex/Articles/Using_Latexdiff_For_Marking_Changes_To_Tex_Documents

\section{rebuttal} % Response2Referees
We greatly appreciate the reviewers for their helpful suggestions and critical comments on our manuscript. The detailed point-by-point reply to the reviewer’s comments are as follows (marked as \textcolor{blue}{blue}). 
And the revised portions in the manuscript are indicated in \textcolor{red}{red}.

@@

Reviewer comments:
%Reviewer #1(Technical Comments to the Author):
%   The ms investigates an interesting and timely topic. However, the discovery cohort involves a small sample size and throughout the analysis, the issue of correcting the obtained p-values for multiple comparisons is not addressed. Hence, the evidence for zooming into TMSB4X is not convincing.

%\section{Responses to Reviewers' comments}
% our responses to the reviewers' comments.
%***Response to reviewer's comments: [藍色字]
\subsection*{1-1}
Comments from the reviewer \#1:

Comments and Suggestions for Authors
The authors have described the effectiveness of RNA sequencing as a tool for exploring prognostic factors; they have also performed a large-scale analysis using the TCGA cohort, which is a very attractive analysis method. I have a few minor questions.
This is an attractive analysis method and I would like to know more details.

1-1) it is generally known that high expression of EGFR is a poor prognostic factor in head and neck cancers, however, why is it that RNA sequencing does not identify RNA coding for EGFR as a poor prognostic factor?
%[我的 candidate 中為什麼沒有 EGFR]

\begin{MyColorPar}{blue}
Answer

We appreciate the reviewer for the critical comments and thank for your agreement of our experiments in the validation phase.....
%[我的 candidate 中為什麼沒有 EGFR]
removed by literature review
citing the line number and exact change, marked in \textcolor{red}{Red from page 6 (line 16) to page 7 (line 17)}
\end{MyColorPar}

\subsection*{1-2}
 DNA alteration (mutation/amplification) is also an influential prognostic factor, but I would like to know if DNA alteration is considered in this analysis.
%[如果加入 DNA alteration 又會如何? 選擇 mRNA 的原因是?]

\begin{MyColorPar}{blue}
Answer

We appreciate the reviewer for the critical comments and thank for your agreement of our experiments in the validation phase.....
a). mRNA study: in drug discovery, the gene expression (overexpression) is much easier to find a candidate for an inhibitory lead (pro-drug?) %比較容易研發

b). => it needs deep learning (DNA+RNA omics study)
\cite{Lawrence2015a} TCGA %的第一篇文章
[see 01/24 google calendar: DNA mutation
Epigenetics in cancer: CpG islands
Lawrence, M. S., Sougnez, C., Lichtenstein, L., Cibulskis, K., Lander, E., Gabriel, S. B., … Pham, M. (2015). Comprehensive genomic characterization of head and neck squamous cell carcinomas. Nature, 517(7536), 576–582. https://doi.org/10.1038/nature14129

The presence of widespread genomic instability in HNSCC, such as cytogenetic aberrations, allelic imbalance/loss of heterozygosity, and microsatellite instability, suggests that there is an imperfection in the host DNA repair machinery. Genomic instability with progressive accumulation of detrimental genetic alterations appears to be dependent upon a circuitous interaction between the environmental genotoxic insults and the host DNA repair machinery, the functional integrity of which is governed by the proper cell cycle control and host DNA repair capacity.
https://www.nature.com/articles/nature14129 Comprehensive genomic characterization of head and neck squamous cell carcinomas
Genomics allows the identification of possibly relevant variants, such as single nucleotide polymorphisms (SNPs), copy number variation (CNV), mutations and translocations => %https://cancersheadneck.biomedcentral.com/articles/10.1186/s41199-020-0047-y

%https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7080958/#SM8 The Landscape of Somatic Copy Number Alterations in Head and Neck Squamous Cell Carcinoma, 2020.
18 GSE dataset + TCGA: chromothripsis 6\%

@@

TMB: To calculate TMB, you need to know the total size of the region sequenced. If data is from exome sequencing, you would find the size of the exome capture, and divide total mutations (or non-synonymous only depending on strategy), by that size (e.g. ~45MB) to get SNV/MB ratio.

ICIs <- TMB <- DDR DNA repair gene
Identification of Genomic Predictors for Treatment Response to Cancer Immunotherapy Using Omics Data Analysis
Yu-Chao Wang

@@

tumor mutational burden-high (TMB-H) [≥10 mutations/megabase (mut/Mb)] solid tumors (for pembrolizumab)

%===================
epigenetic trinity:
%http://www.biomedicine.org.tw/Upload/07_DNA甲基化程度在大腸直腸癌扮演的角色.pdf
%脊椎動物之基因體中約20\%之序列為5'-GC-3' (簡稱CpG)之雙核苷酸(dinucleotide)。然而有 些長約1至2kb之序列段，其CpG含量高達60% (CpG islands)

60\% protein-coding genes with CpG islands on their promoter region

(
McGough JM, Yang D, Huang S, et al. DNA methylation represses IFN-gamma-induced and signal transducer and activator of transcription 1-mediated IFN regulatory factor 8 activation in colon carcinoma cells. Mol Cancer Res 2008;6:1841-1851.
)

methyl CpG-binding domain protein; MBD prevents TF binding on the promoter of gene
=> causing impairment of mismatch repair; MMR => microsatellite instable; MSI

%環境因子的致癌機轉
=>CpG hypermethylation
turn off tumor suppressor genes
and
Hypomethylation turn on oncogene
DKK1
...
hypomethylation ->
loss of gene imprinting
alleles 
..
histone methylation
%http://webcache.googleusercontent.com/search?q=cache:z8zvnjS-C3AJ:sites.mc.ntu.edu.tw/board.php?courseID%3D83%26f%3Ddoc%26folderID%3D581%26cid%3D3060&client=safari&hl=en&gl=tw&strip=1&vwsrc=0
%雖然以上我們討論的是癌症的基因體，但癌症的厲害就是它本來就利用人體原有的生物機制來生存（co-opting），因此，以上在癌症觀察到的基因體複雜性，其實也存在於正常人體.

%從最早，很單純的基因之exon序列，轉錄成mRNA，再轉譯成polypeptide，形成protein，到現在還要考慮epigenetics、mi RNA、TUF (ENCODE將之名為transcripts of unknown function (TUF)=> non-coding RNA 後來很紅)、chromosome environment，基因體的複雜性真是增加了不知多少倍，這也提醒我們在了解基因功能方面，必需更有全面性的關照。這也是「基因體醫學」必需以「基因體科學」為基礎的道理。

%...

%DNA mutation, copy number 增加造成 overexpression of gene

???Answer:
%所以 DNA vs mRNA
high dimensional multi-omics analysis by CNN 
%分析不是獨立變數，彼此有 confounding 放入分析需要使用不同的方法

It may be beneficial to include these different data types in models predicting outcomes, such as the survival time of patients. Until recently, only data from a single omics type were used to build such prediction models, with or without the inclusion of standard clinical data [2]. In recent years, however, the increasing availability of different types of omics data measured for the same patients (called multi-omics data from now on) has led to their combined use for building outcome prediction models. An important characteristic of multi-omics data is the high-dimensionality of the datasets, which frequently have more than 10 000 or even 100 000 variables. This places particular demands on the methods used to build prediction models: they must be able to handle data where the number of variables by far exceeds the number of observations. Moreover, practitioners often prefer sparse and interpretable models containing only a few variables [3]. Last but not the least, multi-omics data are structured: the variables are partitioned into (nonoverlapping) groups. This structure may be taken into account when building prediction models.
%Citation: https://academic.oup.com/bib/advance-article/doi/10.1093/bib/bbaa167/5895463
%特別的 algorithm 
..
Or

@@

DNA mutation:
copy number burden (CNB) and tumor mutation burden (TMB) are important for predicting tumor progression (Marshall et al., 2017; Thomas et al., 2018)
\end{MyColorPar}

%======
\subsection*{2-1}
reviewer \#2

Can be improved
Does the introduction provide sufficient background and include all relevant references? [Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use.] 1) 4)

%[找出其他 database cohort 的比較]
2-1) How representative is the TCGA database for HNSCC?

\begin{MyColorPar}{blue}
Answer

We appreciate the reviewer for the critical comments and thank for your agreement of our experiments in the validation phase.....
%有文章為證1. Lawrence, M. S. et al. Comprehensive genomic characterization of head and neck squamous cell carcinomas. Nature 517, 576–582 (2015).
\cite{Lawrence2015a}
until 2020 1. Wei, R. et al. Analyzing the prognostic value of DKK1 expression in human cancers based on bioinformatics. Ann. Transl. Med. 8, 552 (2020).
\cite{Tang2019}\cite{Wei2020a}
(ok)
\end{MyColorPar}

\subsection*{2-2}
Can be the found positive and negative prognostic genes underlined by comparable studies using other databases than TCGA?

\begin{MyColorPar}{blue}
Answer

We appreciate the reviewer for the critical comments and thank for your agreement of our experiments in the validation phase.....
GSE2837 (GEO) from PrognoScan: http://dna00.bio.kyutech.ac.jp/PrognoScan-cgi/PrognoScan.cgi \cite{Mizuno2009a}
https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB
Relapse Free Survival (RFS) in GSE2837 (not available in the TCGA dataset)
microarray gene expression experiments (Affymetrix X3P chips U133\_X3P)
cohort: VUMC, VAMC, UTMDACC (1992-2005), published on 2006
40 HNSCC samples
cohort n=28 in the following probes of genes with survival significance:
17 out of 20 candidates => 10 genes achieve similar positive and negative prognostic effect comparable with our candidate genes, however, its group separation was be cut by a skewed manner
FCGBP (P-value 0.005658 of KM plot)
FOXA2 (0.001587)

there is survival feature:
A total of 44 patients (22 HNSCC samples and 22 normal samples) were obtained from GSE6631
GSE52793: https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE52793
GSE75537: https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE75537
\end{MyColorPar}

\subsection*{2-3}
Could the authors summarize the elements of the workflow that could be used on any database independently from TCGA?

\begin{MyColorPar}{blue}
Answer

We appreciate the reviewer for the critical comments and thank for your agreement of our experiments in the validation phase.....
Currently, less HNSCC dataset is available worldwide (Indian?) => GEO
generalized use is fine for this workflow, it needs to modify the R code to adapt 
%能否套用在別的 database，可以，但需要 d/l raw microarray or RNA-seq 而且需要標準化(fpkm or RSEM)
It made the messenger \acrshort{rnaseq} matrix with log2 transformed for the downstream analysis, as described in their reference\cite{RSEM2016}.?)
Moreover, we are planning to expand this workflow for pan-cancer studies (other cancer types in the TCGA database).
the elements of the workflow: ...
\end{MyColorPar}

\subsection*{2-4}
Please shortly explain the TCGA database in the Introduction and summarize the advantages of its use.

\begin{MyColorPar}{blue}
Answer

We appreciate the reviewer for the critical comments and thank for your agreement of our experiments in the validation phase.....
*** We modified the introduction according to reviewer's comment...
https://www.cancer.gov/about-nci/organization/ccg/research/structural-genomics/tcga/publications
\end{MyColorPar}

\subsection*{3-1}
reviewer \#3

@@

Must be improved:
Is the research design appropriate?
Are the results clearly presented?
Are the conclusions supported by the results?

3-1) Only computer computing in this research to support 20 candidate biomarkers, DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1, as well as ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, IQCN (previous name as KIAA1683), and NPB, are all heavily associated with the prognosis of OS.

There is little information provided. The authors should provide more evidence to support this article.
%  Once the authors identify TMSB4X as a target, the rest of the analysis seems fine, but their rationale for looking into TMSB4X is not strongly supported by the available data.

\begin{MyColorPar}{blue}
Answer

We appreciate the reviewer for the critical comments and thank for your agreement of our experiments in the validation phase.....
a) Embase searching; %https://www.ncbi.nlm.nih.gov/research/pubtator/?view=docsum&query=CAMK2N1%20head%20and%20neck%20cancer
\cite{Wei2019}
through the PubMed searching, the remark on table 1 and table 2 presents the cancer research articles related to our candidate genes.

@@

% good guy
ZNF557, oncogenic human herpesviruses, EBV and KSHV are silenced by SZF1 and ZNF557, two members of the KRAB-ZFP repressor family\cite{Li2018c}.
ZNF266, % or ZNF16, HZF1?
those genes were reported at following, 
IL19 in esophageal squamous cell carcinoma\cite{Hsing2013},
MYO1H associated mandibular prognathism\cite{Sun2018}, 
FCGBP in thyroid cancer\cite{Griffith2006}, 
?LOC148709?, 
EVPLL in cDNA project,
PNMA5 promotes apoptosis signaling in HeLa and MCF-7 cells\cite{Lee2016}, 
IQCN (previous name as KIAA1683), and 
NPB (Neuropeptide B) is endogenous ligand of the G protein-coupled receptors, named GPR7\cite{Andreis2005}, which is associated with prostate cancer prognosis\cite{Cottrell2007}.

b) (ok) SurvExpress
%試試利用手動找到類似的結果 
Web resource for Biomarker comparison and validation of Survival gene expression data. 
Dataset: HNSC - TCGA Head and Neck squamous cell carcinoma June 2016 (dup=all, data=raw)，(only TCGA June 2016, n=502) \cite{Aguirre-Gamboa2013}
%有類似的結果:
DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, STIP1, DKC1,ZNF557, ZNF266, FCGBP;
%沒有
FOXA2, IL19, MYO1H, LOC148709, EVPLL, PNMA5, IQCN, KIAA1683, NPB
it supposed that ...
%因為 cutoff 不適當，這也就是我們 p-value Tex 的設計目的與強項
 (TCGA)(***please see Figure \label{fig_SurvExpress})

%x c) CCLE_RNAseq_rsem_genes_tpm_20180929.txt.gz
We provide more evidences mentioned above to support the prognostic impact of these candidate genes. It needs to be further validated.
\end{MyColorPar}

### 2021-01-25 rebuttal_responses_revision1.tex

\documentclass[preprint,12pt]{elsarticle}
% major revision and answer question (3 reviewers)
%Sunday, January 24⋅22:30 – 22:55
%Daily, until Jan 29, 2021

% mark in blue or red
\usepackage{xcolor}

\newenvironment{MyColorPar}[1]{%
    \leavevmode\color{#1}\ignorespaces%
}{%
}%

%%% for abbreviations, or acronyms
\usepackage[automake, acronym, nopostdot]{glossaries} 
%\usepackage{glossary-inline}
%\newenvironment{abbreviation}
%\makeglossaries %https://tex.stackexchange.com/questions/110095/list-of-acronyms-is-not-displayed
\newacronym{fdr}{FDR}{false discovery rate}
\newacronym{hpa}{HPA}{the Human Protein Atlas}
\newacronym{hnscc}{HNSCC}{head and neck squamous cell carcinoma}
\newacronym{tcga}{TCGA}{the Cancer Genome Atlas}
\newacronym{tcpa}{TCPA}{the Cancer Proteome Atlas}
\newacronym{rna}{RNA}{ribonucleic acid}
\newacronym{rnaseq}{RNA-Seq}{RNA sequencing}
\newacronym{lncrna}{lncRNA}{long non-coding RNA}
%\newacronym{km}{KM}{Kaplan-Meier}
\newacronym{rppa}{RPPAs}{reverse-phase protein arrays}
\newacronym{rpma}{RPMA}{reverse-phase protein lysate microarray}

\newacronym{mmp}{MMP}{matrix metalloproteinase}
 %DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, and DKC1
 %ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683, and NPB

\newacronym{DKK1}{DKK1}{dickkopf WNT signaling pathway inhibitor 1} 
\newacronym{CAMK2N1}{CAMK2N1}{calcium/calmodulin dependent protein kinase II inhibitor 1} 
\newacronym{STC2}{STC2}{stanniocalcin 2} 
\newacronym{PGK1}{PGK1}{phosphoglycerate kinase 1} 
\newacronym{SURF4}{SURF4}{surfeit 4} 
\newacronym{USP10}{USP10}{ubiquitin specific peptidase 10} 
\newacronym{NEDD4}{NEDD4}{neural precursor cell expressed, developmentally down-regulated 4}
\newacronym{NDFIP1}{NDFIP1}{NEDD4 family interacting protein 1} 
\newacronym{FOXA2}{FOXA2}{forkhead box A2} 
\newacronym{STIP1}{STIP1}{stress-induced-phosphoprotein 1} 
\newacronym{DKC1}{DKC1}{dyskeratosis congenita 1, dyskerin}

\newacronym{ZNF557}{ZNF557}{zinc finger protein 557} 
\newacronym{ZNF266}{ZNF266}{zinc finger protein 266} 
\newacronym{IL19}{IL19}{interleukin 19} 
\newacronym{MYO1H}{MYO1H}{myosin 1H} 
\newacronym{FCGBP}{FCGBP}{Fc fragment of IgG binding protein} 
\newacronym{LOC148709}{LOC148709}{LncRNA LOC148709} 
\newacronym{EVPLL}{EVPLL}{envoplakin-like protein} 
\newacronym{PNMA5}{PNMA5}{paraneoplastic antigen like 5} 
%\newacronym{KIAA1683}{KIAA1683}{IQCN, IQ Motif Containing N} 
\newacronym{IQCN}{IQCN}{IQ motif containing N} % previous name KIAA1683
% "IQ" refers to the first two amino acids of the motif: isoleucine (commonly) and glutamine (invariably)
\newacronym{NPB}{NPB}{neuropeptide B}

 \newacronym{rt}{RT}{radiation therapy}
 \newacronym{nccn}{NCCN}{National Comprehensive Cancer Network}
 \newacronym{hif}{HIF}{hypoxia-inducible factor}
 \newacronym{egfr}{EGFR}{epidermal growth factor receptor}
 \newacronym{ras}{RAS}{rat sarcoma}
 \newacronym{hras}{HRAS}{Harvey rat sarcoma viral oncoprotein}
 \newacronym{erk}{ERK}{extracellular signal-regulated kinases}
 \newacronym{us}{US}{United States}
 \newacronym{fda}{FDA}{Food and Drug Administration}
 \newacronym{tpf}{Tax-PF}{docetaxel, cisplatin, and 5-fluorouracil}
 \newacronym{tki}{TKI}{tyrosine kinase inhibitor}
 \newacronym{her}{HER}{human epidermal growth factor receptor}
 \newacronym{ici}{ICI}{immune-checkpoint inhibitor}
 \newacronym{ctla4}{CTLA-4}{cytotoxic T lymphocyte antigen 4}
 \newacronym{pd1}{PD-1}{programmed death 1}
 \newacronym{pdl1}{PD-L1}{programmed death ligand 1}
 \newacronym{tim3}{TIM-3}{T-cell immunoglobulin mucin protein 3}
 \newacronym{lag3}{LAG-3}{lymphocyte activation gene 3}
 \newacronym{ifng}{IFN-$\gamma$}{interferon gamma}
 \newacronym{tigit}{TIGIT}{T cell immunoglobin and immunoreceptor tyrosine-based inhibitory motif}
 \newacronym{gitr}{GITR}{glucocorticoid-induced tumor necrosis factor receptor}
 \newacronym{vista}{VISTA}{V-domain Ig suppressor of T-cell activation}
 \newacronym{tmsb4x}{TMSB4X}{thymosin beta-4 X-linked}
 \newacronym{emt}{EMT}{epithelial-mesenchymal-transition}
 \newacronym{gdc}{GDC}{Genomic Data Commons}
 \newacronym{nci}{NCI}{the National Cancer Institute}
 \newacronym{gdac}{GDAC}{Genome Data Analysis Center}
 \newacronym{rest}{REST}{Representational State Transfer} 
 \newacronym{api}{API}{Application Programmable Interface}
\newacronym{grch38}{GRCh38}{Genome Reference Consortium Homo sapiens genome assembly 38}
\newacronym{fpkm}{FPKM}{Fragments per kilobase per million reads mapped}
\newacronym{rsem}{RSEM}{RNA-Seq by Expectation-Maximization}
\newacronym{slca}{SLC35E2A}{solute carrier family 35 member E2A}
\newacronym{slcb}{SLC35E2B}{solute carrier family 35 member E2B}
\newacronym{cde}{CDE}{Common Data Element}
\newacronym{id}{ID}{identification}
\newacronym{ajcc}{AJCC}{the American Joint Committee on Cancer}
\newacronym{uicc}{UICC}{he Union for International Cancer Control}
\newacronym{tnm}{TNM}{the tumor size (T), cervical lymph node metastases (N), and distal metastasis status (M)}
\newacronym{ci95}{95\% CI}{95\% confidence interval}
\newacronym{os}{OS}{overall survival}
\newacronym{hr}{HR}{hazard ratio}
\newacronym{hpv}{HPV}{human papillomavirus}
\newacronym{ene}{ENE}{extra-nodal extension}
\newacronym{lvsi}{LVSI}{lymph-vascular space invasion}
\newacronym{pni}{PNI}{perineural invasion}
\newacronym{doi}{DOI}{depth of invasion}
\newacronym{lnd}{LND}{lymph node density}
\newacronym{wpoi5}{WPOI-5}{worst pattern of invasion score 5}
\newacronym{glut4}{GLUT4}{glucose transporters 4}
\newacronym{slc2a4}{SLC2A4}{solute carrier family 2 member A4}
\newacronym{trim24}{TRIM24}{tripartite motif-containing 24}
\newacronym{til}{TIL}{tumor-infiltrating lymphocytes}
\newacronym{tmb}{TMB}{tumor mutational burden}

%==================
\begin{document}

@@

This is an attractive analysis method and I would like to know more details.

1-1) it is generally known that high expression of EGFR is a poor prognostic factor in head and neck cancers, however, why is it that RNA sequencing does not identify RNA coding for EGFR as a poor prognostic factor?

\begin{MyColorPar}{blue}
Answer

We appreciate the reviewer for the critical comments and thank for his/her agreement of our analysis using the TCGA cohort.
%[我的 candidate 中為什麼沒有 EGFR];  
In our analysis, the \acrshort{egfr} is ranked at 5707 from 20500 protein-coding genes %5708-1
by Kaplan-Meier estimate with the log-rank test P-value as 0.0495. The \acrshort{egfr} is identified as one of those poor prognostic factors as well. %However, it is far from the top 20 candidates.
(please see https://github.com/texchi2/pvalueTex/blob/master/HNSCC_OS_marginS_6429.csv for reference, the table was ranked by FDR P-value)

% transforming growth factor- (TGF-α) 
% epidermal growth factor receptor (EGFR)
As in our manuscript mentioned, 
In a multivariate analysis, tumor site, tumor level of \acrshort{egfr}, and tumor level of TGF-$\alpha$ (\acrshort{egfr} ligand) were statistically significant predictors of disease-free survival of \acrshort{hnscc} patients\cite{Rusch1996}\cite{Grandis1998}.
Since that breakthrough discovery and validation, the \acrshort{egfr} monoclonal antibody (cetuximab) and \acrshort{egfr} \acrshort{tki} (such as gefitinib, erlotinib, osimertinib) were developed to treat advanced \acrshort{hnscc}. Although 90\% of \acrshort{hnscc} has overexpression of \acrshort{egfr}, cetuximab has only 10\% to 20\% response rate on those patients\cite{Johnson2020}. So far, cetuximab is still the only drug of choice with proven efficacy, which targeted the selected \acrshort{hnscc} patients\cite{Taberna2019}.
%citing the line number and exact change, marked in \textcolor{red}{Red from page 6 (line 16) to page 7 (line 17)}
Thus, we wish the further validations of our candidate genes to explore more useful drug of choice in the treatment of \acrshort{hnscc} patients.
% a list from literature review, 留 下少於  50 articles mentioned candidates
%HNSCC_survivalAnalysis_marginS_EGFR.Rda
%HNSCC_survivalAnalysis_marginS_EGFR.xlsx
%https://github.com/texchi2/pvalueTex/blob/master/file20500_list.txt
%analysis_export.R to generate https://github.com/texchi2/pvalueTex/blob/master/HNSCC_OS_marginS_6429.csv
\end{MyColorPar}

### 2021-01-27 main.tex
Answer 2-1 done

In summary, identifying predictive biomarkers for selecting standard-of-care or advanced systemic therapy\cite{Cristina2019} in \acrshort{hnscc} is crucial. 
However, there are three challenges of biomarker discovery from survival analysis, so far.
Firstly, although \acrshort{tcga} genomics data were harmonized, there is unclean data, including null expressed genes, which over 50\% of the cohort, should be manually investigated and cleaned.
Second, we need to find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}. Usually, the investigators should get the rationale or revelation of the genes of interest on a specific cancer type. They should upload those genes manually onto bioinformatics tools, such as SurvExpress (http://bioinformatica.mty.itesm.mx:8080/Biomatec/ \newline
SurvivaX.jsp, which has been lost since Oct/2019 and currently out of funds), analyze with \acrshort{tcga} cohort. After downloading the survival results, they could curate plots and tables carefully.
It is not possible to scan the whole human protein-coding genome in this way.
Third, we need to find an optimal cutpoint of those \acrshort{rna} expression data to maximize candidate mining coverage. The above mentioned online tools might set a cutpoint at the median, 1/4 quantile, or 3/4 quantile for subsequent analyses. There are several visualization software or R packages which deal with cutoff determination, such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, Human protein atlas\cite{Uhlen2017}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/ \newline
cutpointr), and cutoffR (available at https://cran.r-project.org/web/
packages/cutoffR). However, non of them could combine the scanning of the protein-coding genes and cutoff optimization programmatically.

@@

The Cancer Genome Atlas (\acrshort{tcga}) profiled 528 \acrshort{hnscc} clinical and genomic data, which has been standardized and available on a unified data portal, \acrfull{gdc} of the \acrfull{nci}.
%\cite{SeanDavis;MartinMorgan2020}
GDC is available at https://portal.gdc.cancer.gov/projects/TCGA-HNSC.
\acrshort{tcga} offers several computational tools to the public for facilitating cancer research.
Broad \acrfull{gdac} Firebrowse (firebrowse.org, version 1.1.35, 2016\_09\_27) is one of those tools to provide data access to each \acrshort{tcga} disease through a \acrfull{rest} \acrfull{api}.
The 528 \acrshort{tcga} \acrshort{hnscc} patients' clinical information and \acrshort{rnaseq} data were obtained from the Firebrowse \acrshort{rest}ful \acrshort{api} with an R package, FirebrowseR (available at https://github.com/mariodeng/\linebreak
FirebrowseR)\cite{Deng2017}. 
We utilized FirebrowseR with our analysis workflow (see Figure \ref{fig:figure1}, step 1) to receive standardized data frames while avoiding data re-formatting, often causing some errors.

@@

\dataavailability{All data process and analyses were performed with R programming language (https://www.r-project.org/, version 4.0.2 2020-06-22) and R packages "firebrowseR", "survival", "reshape", "data.table", "ggplot2", "R.utils", "xlsx", "r2excel", "rJava" and "rms" at Rstudio server (version 1.2.5001) based on Google cloud platform under operation system Linux (Ubuntu LTS, release v18.04.3).
%All the supplementary figures, tables, and R script codes 
The R script codes and datasets generated during the current study are available in the GitHub repository, https://github.com/texchi2/pvalueTex.}

>>>>

In summary, identifying predictive biomarkers for selecting standard-of-care or advanced systemic therapy\cite{Cristina2019} in \acrshort{hnscc} is crucial. 
However, there are three challenges of biomarker discovery from survival analysis, so far.
Firstly, although \acrshort{tcga} genomics data were harmonized, there is unclean data, including null expressed genes, which over 50\% of the cohort, should be manually investigated and cleaned.
Second, we need to find a way to determine candidates from the expression level of 20,500 human protein-coding genes\cite{Clamp2007}. Usually, the investigators should get the rationale or revelation of the genes of interest on a specific cancer type. They should upload those genes manually onto bioinformatics tools, such as SurvExpress (http://bioinformatica.mty.itesm.mx:8080/Biomatec/ \newline
SurvivaX.jsp\cite{Aguirre-Gamboa2013}, which has been lost since Oct/2019 and currently out of funds), analyze with \acrshort{tcga} cohort. After downloading the survival results, they could curate plots and tables carefully.
It is not possible to scan the whole human protein-coding genome in this way.
Third, we need to find an optimal cutpoint of those \acrshort{rna} expression data to maximize candidate mining coverage. The above mentioned online tools might set a cutpoint at the median, 1/4 quantile, or 3/4 quantile for subsequent analyses. There are several visualization software or R packages which deal with cutoff determination, such as Prognoscan\cite{Mizuno2009a}, Cutoff Finder\cite{Budczies2012}, Findcut\cite{Chang2017a}, Human protein atlas\cite{Uhlen2017}, OptimalCutpoints\cite{Cristina2019},  cutpointr (available at https://github.com/thie1e/ \newline
cutpointr), and cutoffR (available at https://cran.r-project.org/web/
packages/cutoffR). However, non of them could combine the scanning of the protein-coding genes and cutoff optimization programmatically.

@@

The Cancer Genome Atlas (\acrshort{tcga}) profiled 528 \acrshort{hnscc} clinical and genomic data, which has been standardized and available at a unified data portal, \acrfull{gdc} of the \acrfull{nci}.
%\cite{SeanDavis;MartinMorgan2020}
GDC is available at https://portal.gdc.cancer.gov/projects/TCGA-HNSC.
\acrshort{tcga} offers several computational tools to the public for facilitating cancer research.
Broad \acrfull{gdac} Firebrowse (firebrowse.org, version 1.1.35, 2016\_09\_27) is one of those tools to provide data access to each \acrshort{tcga} disease through a \acrfull{rest} \acrfull{api}.
The 528 \acrshort{tcga} \acrshort{hnscc} patients' clinical information and \acrshort{rnaseq} data were obtained from the Firebrowse \acrshort{rest}ful \acrshort{api} with an R package, FirebrowseR (available at https://github.com/mariodeng/\linebreak
FirebrowseR)\cite{Deng2017}. 
We utilized FirebrowseR with our analysis workflow (see Figure \ref{fig:figure1}, step 1) to receive standardized data frames while avoiding data re-formatting, often causing some errors.

@@

\dataavailability{All data process and analyses were performed with R programming language (https://www.r-project.org/, version 4.0.2 2020-06-22) and R packages "firebrowseR", "survival", "reshape", "data.table", "ggplot2", "R.utils", "xlsx", "r2excel", "rJava" and "rms" at Rstudio server (version 1.2.5001) based on Google cloud platform under operation system Linux (Ubuntu LTS, release v18.04.3).
%All the supplementary figures, tables, and R script codes 
The R script codes and datasets generated during the current study are available at the GitHub repository, https://github.com/texchi2/pvalueTex.}
